\documentclass[main.tex]{subfiles}
\begin{document}

\chapter{Others}
\section{考研复试用}
\subsection{self-introduction}
Good morning, every teacher here, My name is Shaoqun Liu, a student majoring in Software Engineering currently at the Shandong University of Technology. I am a student of wide interests that extended beyond Java web backend development to cybersecurity and machine learning. It is worth mentioning that I am a strong advocate of open-source software. I think I have gotten a lot of education of developing a web application in my undergraduate career so that I want to study something more challenging and more novel in the future postgraduate career. As we all know, Artificial Intelligence is a rising field of computer science. It provides a new idea and a new approach to solve those problems hard to program using a traditional programming method. It makes the computer think like a human through some mysterious things called neural-network. I have tried to understand some algorithms of machine learning which also considered as a subset of the study of artificial intelligence through Google Open Online Education and Netease open class, but all failed. I think the main obstacle between me and understanding those algorithms is firstly the lack of mathematics knowledge and secondly the lack of a good study environment with a nice teacher to talk about. So, that is the reason why I'm standing here and looking for an opportunity to study and research in this field with someone maybe present in this room. And, I will be very honored if you can grant me the opportunity to study in here. Thank you!

\subsection{something to do after graduation}
I hope I can join an international giant company to work for researching after graduation, such as Microsoft Research Asia or Google Brain Project. If those companies or projects still require a higher degree by that time, I think I will prepare my doctoral entrance exam and continue my career of exploration of computer science.

\subsection{about the choice of this major}
It just because I'm majoring in Software Engineering in my undergraduate career. I love this major. The rise of the study of computer science is really changing the world from the past to the future. The internet, artificial intelligence, big data, and quantum computing definitely enriching the quality of we human beings live. As a sunrise industry, it easy to be employed and lead me to a relatively higher wage after graduation.

\subsection{what is your greatest strength}
Obviously, my strongest asset is I'm young. My brain allows me to study and remember more things. My body allows me to go further and insight into the big world. I have all objective conditions to explore in depth.

\section{找工作用}
\subsection{自我介绍}
我叫刘少群，目前就读于山东理工大学计算机学院软件工程专业，而且还是XX大学计算机学院的准研究生。目前打算应聘贵公司YY实习生岗位。我在本科期间曾加入计算机学院校企协同创新实验室，在实验室的研究方向为企业级应用软件开发。曾作为项目负责人带领一个4个人的小团队，主持开发2017年度国家级大学生创新创业项目，在这期间我主要负责Java服务端开发，与团队成员协调开发事宜以及前后端接口的统一和规范，以及与指导老师2人协调项目的开发进度、经费报销等。该项目一共获得国家资助的科研经费1万元，并于2018年10月通过结项答辩，成功结项。

\end{document}
